Considering scale in multilayer animal social networks

### 2020-06-18 paper/manuscript.Rmd
rm source bc of self invalidation
fix smashed pars and sentences from comments

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

Increasing land cover resolution resulted in decreased availability of foraging habitat 
<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
refers to the thing an animal is eating-->,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). <!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again. I think this should be reordered so it's easier to follow. -->
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

@@

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments.<!--  <- long sentence with two coulds -->For example, social processes may be an 
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

Increasing land cover resolution resulted in decreased availability of foraging habitat 
<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
refers to the thing an animal is eating-->,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). <!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again. I think this should be reordered so it's easier to follow. -->
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

@@

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments.<!--  <- long sentence with two coulds --> For example, social processes may be an 
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
